\documentclass[18pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage[T1]{fontenc}
\usepackage{libertine}

\setlength\parskip{\bigskipamount}
\setlength\parindent{0pt}
\pagestyle{empty}

\begin{document}

\enlargethispage{4em}

\vspace*{-3em}

\begin{center}
\large \textbf{A classical logic fairy tale}
\end{center}

\textbf{Narrator.} Once upon a time, in a kingdom far, far away, the queen of
the land and of all Möbius strips called for her royal philosopher.

\textbf{Queen.}
Philosopher! I ask you to carry out the following order. Get me the
Philosopher's Stone, or alternatively find out how one could produce arbitrary
amounts of gold with it!

\textbf{Philosopher.}
But my queen! I haven't studied anything useful! How could I fulfill this order?

\textbf{Queen.}
That is not my concern. I'll see you again tomorrow. Should you not accomplish
the task, I will take your head off.

\textbf{Narrator.}
After a long and wakeful night the philosopher was called to the queen again.

\textbf{Queen.}
Tell me! What do you have to report?

\textbf{Philosopher.}
It was not easy and I needed to consult lots of books, but finally I actually
found out how to use the Philosopher's Stone to produce arbitrary amounts of
gold. But only I can conduct this procedure, your royal highness.

\textbf{Queen.}
Alright. So be it.

\textbf{Narrator.}
And so years passed by, during which the philosopher imagined himself to be
safe. The queen searched for the stone on her own, but as long as she hadn't
found it, the philosopher didn't need to worry. Yet one day the impossible
happened: The queen has found the stone! And prompty called for her philosopher.

\textbf{Queen.}
Philosopher, look! I have found the Philosopher's Stone! Now live up to your
promise! \emph{[She hands over the stone.]}

\textbf{Philosopher.}
Thank you. \emph{[He inspects the stone.]} This is indeed the Philosopher's
Stone. Many years ago you asked me to either acquire the Philosopher's Stone or
find out how to produce arbitrary amounts of gold using it. Now it's my
pleasure to present to you the Philosopher's Stone. \emph{[He returns the stone.]}

\end{document}
